### 2019-09-25 paper/paper.tex
Update paper.tex

\begin{figure}
    \begin{minipage}{0.5\textwidth}
    \begin{lstlisting}[
    framesep=2mm,
    ]{Julia}
    function $\mathcal{J}$($f \circ g$)(x)
        $a$, $\underline{a}$ = $\mathcal{J}(f)(x)$
        $b$, $\underline{b}$ = $\mathcal{J}(g)(a)$
        $b$, $z$ $\to$ begin
            $\underline{a}$($\underline{b}$(z))
        end
    end
    \end{lstlisting}
    % \begin{verbatim}
    % function J(f . g)(x)
    %     a, da = J(f)(x)
    %     b, db = J(g)(a)
    %     b, z -> da(db(z))
    % end
    % \end{verbatim}
    \caption{The differential operator $\mathcal{J}$ is able to implement the chain rule through a local, syntactic recursive transformation.}\label{chain}
    \end{minipage}
    \hspace{0.1in}
    \begin{minipage}{0.5\textwidth}
    \begin{lstlisting}[
    framesep=2mm,
    fontsize=\footnotesize,
    fontfamily=fdm,
    xleftmargin=6pt,
    escapeinside=,mathescape=true
    ]{Julia}
    julia> f(x) = x^2 + 3x + 1
    julia> gradient(f, 1/3)
    (3.6666666666666665,)

@@

\begin{table}[]
\centering
\begin{tabular}{cccc}
Layers & Total Overhead & Number of Ops & Overhead/op \\ \hline
1      & 147.0 us & 255 & 576.3 ns \\
2      & 280.5 us & 491 & 571.3 ns \\ 
3      & 406.1 us & 727 & 558.6 ns \\ \hline
\end{tabular}
\label{table:zygote_overhead}
\caption{\Zygote\ per-op overhead estimated across varying numbers of stacked LSTM layers.}
\end{table}

@@

\begin{comment}

\subsection{Combining Probabilistic Programming with Photo-Realistic Computer Vision}
\label{comp-vis}

Here we show how to construct custom \texttt{UniformRGB} and \texttt{NormalRGB} distributions and their log PDFs. We combine this with the Turing probabilistic programming language, defining a generative model of an image where $\mu \sim \textnormal{UniformRGB}()$ and each $\textnormal{pixel} \sim \textnormal{NormalRGB}(\mu, \sigma)$.

Aside from the correctness and usability benefits of having neural networks operate using types, rather than huge N-dimensional number-bags, there is an opportunity to take advantage of existing color science rather than re-learning from scratch. For example, work in natural language processing and colours typically assume a naive Euclidean loss in the RGB space; they can now use accurate perceptual losses or work in color spaces representing the various forms of color blindness. This is the essence of differentiable programming.

%This methodology scales to full photo-realistic renderers.
An emerging direction for computer vision is the notion of  `inverse graphics': where vision models take pixel arrays to scene parameters, renderers take scene parameters to pixel arrays. Many high-fidelity, photo-realistic renderers are available which contain a vast amount of implicit knowledge. Differentiation allows renderers and models to be used in an autoencoder-like setup to quickly bootstrap a full vision model.

As in other cases, the difficulty lies in getting efficient derivatives from a production-ready renderer, typically written in a performance language like C++. We repeat the going themes of this paper: ML framework-based reimplementations are typically limited compared to existing renderers (both by the available framework operations and by the years of work from rendering experts that has gone into production renderers), and workarounds such as Monte Carlo sampling impose a high efficiency cost (around $40\times$ slower than a single render) compared to AD (at most around ~$5\times$ due to division, in principle). The Julia community's approach is to build a renderer suitable for traditional production rendering tasks, using a general and high-performance numerical language, and then differentiate it.

\begin{lstlisting}[
    frame=lines,
    framesep=2mm,
    fontsize=\footnotesize,
    fontfamily=fdm,
    xleftmargin=6pt,
    escapeinside=,mathescape=true
    ]{Julia}
julia> guess = PointLight(Vec3(1.0), 20000.0, Vec3(1.0, 2.0, -7.0))

julia> function loss_function(light)
           rendered_color = raytrace(origin, direction, scene, light, eye_pos)
           rendered_img = process_image(rendered_color, screen_size.w,
                                        screen_size.h)
           return mean((rendered_img .- reference_img).^2)
       end

julia> gs = gradient(x -> loss_function(x, image), guess)   
\end{lstlisting}

In our examples we have used our prototype renderer to demonstrate optimization of the position of a point light source, given the desired final rendered image. We define a loss function that accepts a point light source as input, renders the scene, and compares it to a reference image. As usual, gradients are then trivial and we can begin to update the position of the point source.

\end{comment}

>>>>

\begin{figure}
    \begin{minipage}{0.5\textwidth}
    \begin{lstlisting}[
    framesep=2mm,
    ]{Julia}
    function $\mathcal{J}$($f \circ g$)(x)
        $a$, $\underline{a}$ = $\mathcal{J}(f)(x)$
        $b$, $\underline{b}$ = $\mathcal{J}(g)(a)$
        $b$, $z$ $\to$ begin
            $\underline{a}$($\underline{b}$(z))
        end
    end
    \end{lstlisting}
    % \begin{verbatim}
    % function J(f . g)(x)
    %     a, da = J(f)(x)
    %     b, db = J(g)(a)
    %     b, z -> da(db(z))
    % end
    % \end{verbatim}
    \caption{The differential operator $\mathcal{J}$ is able to implement the chain rule through a local, syntactic recursive transformation.}\label{chain}
    \end{minipage}
    \hspace{0.1in}
    \begin{minipage}{0.5\textwidth}
    % \begin{lstlisting}
    % [
    % framesep=2mm,
    % fontsize=\footnotesize,
    % fontfamily=fdm,
    % xleftmargin=6pt,
    % escapeinside=,mathescape=true
    % ]{Julia}
    \begin{lstlisting}
    julia> f(x) = x^2 + 3x + 1
    julia> gradient(f, 1/3)
    (3.6666666666666665,)

@@

\begin{table}[]
\centering
\begin{tabular}{cccc}
Layers & Total Overhead & Number of Ops & Overhead/op \\ \hline
1      & 147.0 us & 255 & 576.3 ns \\
2      & 280.5 us & 491 & 571.3 ns \\ 
3      & 406.1 us & 727 & 558.6 ns \\ \hline
\end{tabular}
\caption{\Zygote\ per-op overhead estimated across varying numbers of stacked LSTM layers.}
\label{table:zygote_overhead}
\end{table}

@@

% \begin{comment}

% \subsection{Combining Probabilistic Programming with Photo-Realistic Computer Vision}
% \label{comp-vis}

% Here we show how to construct custom \texttt{UniformRGB} and \texttt{NormalRGB} distributions and their log PDFs. We combine this with the Turing probabilistic programming language, defining a generative model of an image where $\mu \sim \textnormal{UniformRGB}()$ and each $\textnormal{pixel} \sim \textnormal{NormalRGB}(\mu, \sigma)$.

% Aside from the correctness and usability benefits of having neural networks operate using types, rather than huge N-dimensional number-bags, there is an opportunity to take advantage of existing color science rather than re-learning from scratch. For example, work in natural language processing and colours typically assume a naive Euclidean loss in the RGB space; they can now use accurate perceptual losses or work in color spaces representing the various forms of color blindness. This is the essence of differentiable programming.

% %This methodology scales to full photo-realistic renderers.
% An emerging direction for computer vision is the notion of  `inverse graphics': where vision models take pixel arrays to scene parameters, renderers take scene parameters to pixel arrays. Many high-fidelity, photo-realistic renderers are available which contain a vast amount of implicit knowledge. Differentiation allows renderers and models to be used in an autoencoder-like setup to quickly bootstrap a full vision model.

% As in other cases, the difficulty lies in getting efficient derivatives from a production-ready renderer, typically written in a performance language like C++. We repeat the going themes of this paper: ML framework-based reimplementations are typically limited compared to existing renderers (both by the available framework operations and by the years of work from rendering experts that has gone into production renderers), and workarounds such as Monte Carlo sampling impose a high efficiency cost (around $40\times$ slower than a single render) compared to AD (at most around ~$5\times$ due to division, in principle). The Julia community's approach is to build a renderer suitable for traditional production rendering tasks, using a general and high-performance numerical language, and then differentiate it.

% \begin{lstlisting}[
%     frame=lines,
%     framesep=2mm,
%     fontsize=\footnotesize,
%     fontfamily=fdm,
%     xleftmargin=6pt,
%     escapeinside=,mathescape=true
%     ]{Julia}
% julia> guess = PointLight(Vec3(1.0), 20000.0, Vec3(1.0, 2.0, -7.0))

% julia> function loss_function(light)
%           rendered_color = raytrace(origin, direction, scene, light, eye_pos)
%           rendered_img = process_image(rendered_color, screen_size.w,
%                                         screen_size.h)
%           return mean((rendered_img .- reference_img).^2)
%       end

% julia> gs = gradient(x -> loss_function(x, image), guess)   
% \end{lstlisting}

% In our examples we have used our prototype renderer to demonstrate optimization of the position of a point light source, given the desired final rendered image. We define a loss function that accepts a point light source as input, renders the scene, and compares it to a reference image. As usual, gradients are then trivial and we can begin to update the position of the point source.

% \begin{figure}[!htb]
% \minipage{0.32\textwidth}
%   \includegraphics[width=\linewidth]{images/triangle_initial_guess.jpg}
%   \caption{Initial Guess}\label{fig:raytracer1}
% \endminipage\hfill
% \minipage{0.32\textwidth}
%   \includegraphics[width=\linewidth]{images/triangle_100.jpg}
%   \caption{After 100 iterations}\label{fig:raytracer2}
% \endminipage\hfill
% \minipage{0.32\textwidth}%
%   \includegraphics[width=\linewidth]{images/triangle_original.jpg}
%   \caption{Target Image}\label{fig:raytracer3}
% \endminipage
% \end{figure}

% \end{comment}
